Decision Support and Health Insurance Choice

### 2020-09-02 Paper.tex
change bibtex link

\title{Decision Support and Health Insurance Choice}
\author{Ian McCarthy \& Evan Saltzman}
\date{April 30, 2020}

@@

Our final dataset consists of 3,200,080 household/year observations from the California health insurance exhanges from 2014 to 2019. Our data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any). From these data, we can identify each household's set of possible health insurance plans, and we employ premium and cost sharing subsidy formulas to calculate health insurance costs for each possible plan for each household.

@@

Our nested logit models establish strong evidence that decision assistance matters for insurance choice. Turning specifically to dominated choices, our baseline results suggest that individuals with decision assistance are 1.16 percentage points less likely to make a dominated choice. On a base of 2.8\%, this reflects a 41\% decrease in the probability of making a dominated choice.

We also find evidence fo heterogeneities in the effects of different forms of decision assistance. In particular, we find that individuals using publicly provided decision assistance are 0.91 percentage points less likely to select a dominated plan, while individuals using a private insurance agent are 1.26 percentage points less likely to select a dominated plan.

>>>>

\title{Decision Support and Health Insurance Choice}
\author{Ian McCarthy \& Evan Saltzman}
\date{September 02, 2020}

@@

Our final dataset consists of 3,212,732 household/year observations from the California health insurance exhanges from 2014 to 2019. Our data include a variety of household characteristics, plan choices and plan characteristics, and information on the type of decision assistance used by the enrollee (if any). From these data, we can identify each household's set of possible health insurance plans, and we employ premium and cost sharing subsidy formulas to calculate health insurance costs for each possible plan for each household

@@

Our nested logit models establish strong evidence that decision assistance matters for insurance choice. Turning specifically to dominated choices, our baseline results suggest that individuals with decision assistance are 1.4 percentage points less likely to make a dominated choice. On a base of 2.8\%, this reflects a 50\% decrease in the probability of making a dominated choice.

We also find evidence fo heterogeneities in the effects of different forms of decision assistance. In particular, we find that individuals using publicly provided decision assistance are 1.09 percentage points less likely to select a dominated plan, while individuals using a private insurance agent are 1.54 percentage points less likely to select a dominated plan.
